Comparison between baseline and test performance

### 2022-10-06 analysis/baseline.Rmd
update figures
Signed-off-by: Atsuko Tominaga <Tominaga_Atsuko@phd.ceu.edu>

# perform the function above
res_bl <- lapply(dt2.list, label)

@@

# IOI 
## 1. Individual
```{r ioi}
# for each individual
ioi_trial <- dt_ioi[, .(N = .N, Mean = mean(IOI), SD = sd(IOI)), by = .(SubNr, TrialNr, Stimuli, Articulation, Dynamics, Category)]

@@

```{r ioi-all-plot}
ggboxplot(ioi, "Articulation", "Mean", color = "Dynamics", add = "jitter", xlab = "Articulation", ylab = "IOIs (ms)", title = "IOI")
```

@@

```{r}
aov_ez(
  data = ioi,
  id = "SubNr",
  dv = "Mean",
  within = c("Category")
)
```

@@

```{r kot, echo = FALSE}
# for each individual
kot_trial <- dt_kot[Subcomponent1 == "Legato" | Subcomponent1 == "Staccato", .(N = .N, Mean = mean(KOT), SD = sd(KOT)), by = .(SubNr, TrialNr, Stimuli, Articulation, Dynamics, Category, Subcomponent1)]

>>>>

# perform the function above
res_bl <- lapply(dt2.list, label_bl)

@@

# IOI 
## 1. Individual
```{r ioi}
# for each individual
dt_ioi$Articulation <- factor(dt_ioi$Articulation, c("Present", "Absent", "Baseline"))
dt_ioi$Dynamics <- factor(dt_ioi$Dynamics, c("Present", "Absent", "Baseline"))

ioi_trial <- dt_ioi[, .(N = .N, Mean = mean(IOI), SD = sd(IOI)), by = .(SubNr, TrialNr, Stimuli, Articulation, Dynamics, Category)]

@@

```{r ioi-all-plot}
ggplot(ioi, aes(x = Articulation, y = Mean, color = Dynamics))+ 
  geom_boxplot(position = position_dodge2(preserve = "single")) +
  geom_point(binaxis = "y", stackdir = "center", position = position_dodge(0.75)) +
  theme_pubr()
#ggboxplot(ioi, "Articulation", "Mean", color = "Dynamics", add = "jitter", xlab = "Articulation", ylab = "IOIs (ms)", title = "IOI")
```

@@

```{r}
aov_ez(
  data = ioi[Category != "baseline"],
  id = "SubNr",
  dv = "Mean",
  within = c("Articulation", "Dynamics")
)
```

@@

```{r kot, echo = FALSE}
# for each individual
dt_kot$Articulation <- factor(dt_kot$Articulation, c("Present", "Absent", "Baseline"))
dt_kot$Dynamics <- factor(dt_kot$Dynamics, c("Present", "Absent", "Baseline"))

kot_trial <- dt_kot[Subcomponent1 == "Legato" | Subcomponent1 == "Staccato", .(N = .N, Mean = mean(KOT), SD = sd(KOT)), by = .(SubNr, TrialNr, Stimuli, Articulation, Dynamics, Category, Subcomponent1)]
